Type-cones of $\b{g}$-vector fans

### 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
added notes on Minkowski sums

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray, overpic}
\usepackage[noabbrev,capitalise]{cleveref}
\usepackage[normalem]{ulem}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}{figures/walks/}{figures/tubes/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}

@@

% others
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\newcommand{\Eg}{\textit{E.g.}~} % exempli gratia
\newcommand{\apriori}{\textit{a priori}} % a priori
\newcommand{\viceversa}{\textit{vice versa}} % vice versa
\newcommand{\versus}{\textit{vs.}~} % versus
\newcommand{\aka}{\textit{a.k.a.}~} % also known as
\newcommand{\perse}{\textit{per se}} % per se
\newcommand{\ordinal}{\textsuperscript{th}} % th for ordinals
\newcommand{\ordinalst}{\textsuperscript{st}} % st for ordinals
\definecolor{darkblue}{rgb}{0,0,0.7} % darkblue color
\definecolor{green}{RGB}{57,181,74} % green color
\definecolor{violet}{RGB}{147,39,143} % violet color
\newcommand{\red}{\color{red}} % red command
\newcommand{\blue}{\color{blue}} % blue command
\newcommand{\orange}{\color{orange}} % orange command
\newcommand{\green}{\color{green}} % green command
\newcommand{\darkblue}{\color{darkblue}} % darkblue command
\newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
\newcommand{\para}[1]{\medskip\noindent\uline{\textit{#1.}}} % paragraph
\renewcommand{\topfraction}{1} % possibility to have one page of pictures
\renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
\newcommand{\ex}{_{\textrm{exm}}} % examples
\newcommand{\pa}{_{\textrm{pa}}} % path
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=1pt, scale=.7] (char) {#1};}}
\newcommand{\compactVector}[3]{\begin{bmatrix} #1 \\[-.1cm] #2 \\[-.1cm] #3 \end{bmatrix}}

@@

% Type cone
\newcommand{\typeCone}{\mathbb{TC}} % type cone
\newcommand{\compatibilityDegree}[2]{(#1\,\|\,#2)} % compatibility degree
\newcommandx{\coefficient}[3][1={\ray[s]}, 2=\ray, 3=\ray']{\alpha_{#2,#3}(#1)} % coefficient in linear dependence

@@

\title{Type cones of $\b{g}$-vector fans}

@@

\begin{abstract}
We investigate the type cone of the $\b{g}$-vector fans for different generalizations of the associahedron (hopefully generalized associahedra, gentle associahedra, graph associahedra, and maybe quotientopes and brick polytopes).
The objective is to determine which are the exchangeable pairs of objects that describe the type cone.
When the type cone happens to be simplicial, we derive simple descriptions of all polytopal realizations of the $\b{g}$-vector fan.
\end{abstract}

@@

\section{Polytopal realizations and type cone of a simplicial fan}

@@

We denote by~$\R_{\ge0}\rays \eqdef \set{\sum_{\ray \in \rays} \lambda_{\ray} \, \ray}{\lambda_{\ray} \in \R_{\ge0}}$ the \defn{positive span} of a set~$\rays$ of vectors of~$\R^d$.
A \defn{polyhedral cone} is a subset of~$\R^d$ defined equivalently as the positive span of finitely many vectors or as the intersection of finitely many closed linear halfspaces.
The \defn{faces} of a cone~$C$ are the intersections of~$C$ with the supporting hyperplanes of~$C$.
The $1$-dimensional (resp.~codimension~$1$) faces of~$C$ are called~\defn{rays} (resp.~\defn{facets}) of~$C$.
A cone is \defn{simplicial} if it is generated by a set of independent vectors.

@@

\subsection{Type cone}

@@

\begin{proposition}
\label{prop:characterizationPolytopalFan}
Then the following are equivalent for any height vector~$h \in \R^N$:
\begin{enumerate}
\item The fan~$\Fan$ is the normal fan of the polytope~$P_\b{h} \eqdef \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$.
\item For any two adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ with~$\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$,
\[
\alpha \, h_{\ray} + \alpha' \, h_{\ray'} + \sum_{\ray[s] \in \rays \cap \rays'} \beta_{\ray[s]} \, h_{\ray[s]} > 0,
\]
where
\[
\alpha \, \ray + \alpha' \, \ray' + \sum_{\ray[s] \in \rays \cap \rays'} \beta_{\ray[s]} \, \ray[s] = 0
\]
is the unique (up to rescaling) linear dependence with~$\alpha, \alpha' > 0$ between the rays of~$\rays \cup \rays'$.
\end{enumerate}
\end{proposition}

@@

In this paper, we are interested in the set of all possible realizations of~$\Fan$. This was studied by P.~McMullen in~\cite{McMullen-typeCone}.

\begin{definition}
The \defn{type cone} of~$\Fan$ is the cone~$\typeCone(\Fan)$ of all $\Fan$-admissible height vectors~$\b{h}$:
\begin{align*}
\typeCone(\Fan) & \eqdef \set{\b{h} \in \R^N}{\Fan \text{ is the normal fan of } P_\b{h}} \\
& = \Bigset{\b{h} \in \R^N}{\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0 \; \begin{array}{l} \text{for any adjacent maximal} \\ \text{cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$} \end{array}}.
\end{align*}
\end{definition}

Note that the type cone is an open cone and contains a linearity subspace of dimension~$n$ (it is invariant by translation in~$\b{G} \R^n$). We could thus intersect~$\typeCone(\Fan)$ by the kernel of~$\b{G}$, or consider the projection~$\b{K}\typeCone(\Fan)$.

\begin{definition}
An \defn{extremal adjacent pair} of~$\Fan$ is a pair of adjacent maximal cones~$\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ of~$\Fan$ such that the corresponding inequality $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0$ in the definition of the type cone~$\typeCone(\Fan)$ actually defines a facet of~$\typeCone(\Fan)$.
\end{definition}

In other words, extremal adjacent pairs define the extremal rays of the polar of the type cone~$\typeCone(\Fan)$.
Understanding the extremal adjacent pairs of~$\Fan$ enables to describe its type cone~$\typeCone(\Fan)$ and thus all its polytopal realizations.

\begin{remark}
\label{rem:dimTypeCone}
Since the type cone is an open~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets.
We say that the type cone is \defn{simplicial} when it has precisely $N-n$ facets.
\end{remark}

@@

\begin{definition}
\label{def:uerp}
We say that two exchangeable rays~$\ray, \ray'$ of~$\Fan$ admit a \defn{unique exchange relation} when the linear dependence
\[
\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \ray[s] = 0.
\]
does not depend on the pair~$\{\rays, \rays'\}$ of adjacent maximal cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, but only on the pair of rays~$\ray, \ray'$.
This implies in particular that the rays~$\ray[s]$ for which~$\coefficient[{\ray[s]}][\rays][\rays'] \ne 0$ belong to~$\rays \cup \rays'$ for any pair~$\{\rays, \rays'\}$ of adjacent cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$. These rays are thus called \defn{forced rays} for the exchangeable pair~$\{\ray, \ray'\}$.

We say that the fan~$\Fan$ has the \defn{unique exchange property} if any two exchangeable rays~$\ray, \ray'$ of~$\Fan$ admit a unique exchange relation
\end{definition}

When~$\Fan$ has the unique exchange relation property, we change the notation~$\coefficient[{\ray[s]}][\rays][\rays']$ to~$\coefficient$ and we obtain that the type cone of~$\Fan$ is expressed as
\[
\typeCone(\Fan) = \Bigset{\b{h} \in \R^N}{\sum_{\ray[s] \in \rays \cup \rays'} \coefficient \, \b{h}_{\ray[s]} > 0 \text{ for any exchangeable rays~$\ray$ and~$\ray'$ of~$\Fan$}}.
\]

\begin{definition}
In a fan~$\Fan$ with the unique exchange relation property, an \defn{extremal exchangeable pair} is a pair of exchangeable rays~$\{\ray,\ray'\}$ such that the corresponding inequality~${\sum_{\ray[s] \in \rays \cup \rays'} \coefficient \, \b{h}_{\ray[s]} > 0}$ defines a facet of the type cone~$\typeCone(\Fan)$.
\end{definition}

@@

In this section, we provide alternative polytopal realizations of the fan~$\Fan$.
We also discuss the behavior of these realizations in the situation when the type cone~$\typeCone(\Fan)$ is simplicial.

@@

\begin{corollary}
\label{coro:simplicialTypeCone}
Assume that the type cone~$\typeCone(\Fan)$ is simplicial and let~$\b{K}$ be the $(N-n) \times N$-matrix whose rows are the outer normal vectors of the facets of~$\typeCone(\Fan)$. Then the polytope
\[
R_\b{\ell} \eqdef \set{\b{z} \in \R^N}{K\b{z} = \b{\ell} \text{ and } \b{z} \ge 0}
\]
is a realization of the fan~$\Fan$ for any positive vector~$\b{\ell} \in \R_{>0}^{N-n}$.
Moreover, the polytopes~$R_\b{\ell}$ for~$\b{\ell} \in \R_{>0}^{N-n}$ describe all polytopal realizations of~$\Fan$.
\end{corollary}

\begin{proof}
Let~$\b{\ell} \in \R_{>0}^{N-n}$.
Since~$\b{K}$ has full rank there exists~$\b{h} \in \R^N$ such that~$\b{K}\b{h} = \b{\ell}$.
Since~$\b{K}\b{h} \ge 0$ and the rows of~$\b{K}$ are precisely all outer normal vectors of the facets of the type cone~$\typeCone(\Fan)$, we obtain that~$\b{h}$ belongs to~$\typeCone(\Fan)$.
Since $R_\b{\ell} = Q_\b{h} \sim P_\b{h}$ by \cref{prop:alternativePolytopalRealization}, we conclude that~$R_\b{\ell}$ is a polytopal realization of~$\Fan$.
Since~$\typeCone(\Fan)$ is simplicial, we have~$\b{K}\typeCone(\Fan) = \R_{>0}^{N-n}$, so that we obtain all polytopal realizations of~$\Fan$ this way.
\end{proof}

@@

\subsection{Faces of the type cone and Minkowski sums}

@@

\cref{lem:MinkowskiSum} ensures that convex combinations in the type cone correspond to Minkowski combinations of polytopes. This provides natural Minkowski summands for all polytopal realizations of~$\Fan$.

\begin{corollary}
Any polytope in~$\typeCone(\Fan)$ is the Minkowski sum of at most~$N-n$ polytopes corresponding to the rays of~$\b{K}\typeCone(\Fan)$.
\end{corollary}

@@

In this section, we study the type cones of complete simplicial fans arising as normal fans of three families of generalizations of the associahedron: the generalized associahedra of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, FominZelevinsky-ClusterAlgebrasIV, HohlwegLangeThomas, HohlwegPilaudStella}, the gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing}, and the graph associahedra~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}. 
All these families contain the classical associahedra~$\Asso[n]$ constructed in~\cite{ShniderSternberg, Loday}.

@@

We first describe the associahedra of~\cite{ShniderSternberg, Loday} and their type cones as they are the prototypes of our constructions.

@@

\subsubsection{Type cones of associahedra}

From the linear dependencies of \cref{prop:exchangeablePairsAsso}, we obtain a redundant description of the type cone of the fan~$\gvectorFan[n]$.

\begin{corollary}
\label{coro:typeConeAsso}
Let~$n \in \N$ and~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$. Then the type cone of the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$ is given by
\[
\typeCone(\gvectorFan[n]) = \set{\b{h} \in \R^{X(n)}}{\begin{array}{l} \b{h}_{(0,n+2)} = 0, \qquad\text{and}\qquad \b{h}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{h}_{(a,b)} + \b{h}_{(a',b')} > \b{h}_{(a,b')} + \b{h}_{(a',b)} \text{ for all } 0 \le a < a' < b < b' \le n+2 \end{array}}.
\]
\end{corollary}

We now describe the facets of this type cone~$\typeCone(\gvectorFan[n])$.

@@

\begin{corollary}
\label{coro:simplicialTypeConeAsso}
The type cone~$\typeCone(\gvectorFan[n])$ is simplicial.
\end{corollary}

@@

\begin{corollary}
\label{coro:simplicialTypeConeCA}
The type cone~$\typeCone(\gvectorFan[n])$ is simplicial.
\end{corollary}

>>>>

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray, overpic}
\usepackage[noabbrev,capitalise]{cleveref}
\usepackage[normalem]{ulem}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}

@@

% others
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\newcommand{\Eg}{\textit{E.g.}~} % exempli gratia
\newcommand{\apriori}{\textit{a priori}} % a priori
\newcommand{\viceversa}{\textit{vice versa}} % vice versa
\newcommand{\versus}{\textit{vs.}~} % versus
\newcommand{\aka}{\textit{a.k.a.}~} % also known as
\newcommand{\perse}{\textit{per se}} % per se
\newcommand{\ordinal}{\textsuperscript{th}} % th for ordinals
\newcommand{\ordinalst}{\textsuperscript{st}} % st for ordinals
\definecolor{darkblue}{rgb}{0,0,0.7} % darkblue color
\definecolor{green}{RGB}{57,181,74} % green color
\definecolor{violet}{RGB}{147,39,143} % violet color
\newcommand{\red}{\color{red}} % red command
\newcommand{\blue}{\color{blue}} % blue command
\newcommand{\orange}{\color{orange}} % orange command
\newcommand{\green}{\color{green}} % green command
\newcommand{\darkblue}{\color{darkblue}} % darkblue command
\newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
\newcommand{\para}[1]{\medskip\noindent\uline{\textit{#1.}}} % paragraph
\renewcommand{\topfraction}{1} % possibility to have one page of pictures
\renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
\newcommand{\ex}{_{\textrm{exm}}} % examples
\newcommand{\pa}{_{\textrm{pa}}} % path
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=1pt, scale=.7] (char) {#1};}}

@@

% Type-cone
\newcommand{\typeCone}{\mathbb{TC}} % type-cone
\newcommand{\ctypeCone}{\overline{\mathbb{TC}}} % type-cone
\newcommand{\compatibilityDegree}[2]{(#1\,\|\,#2)} % compatibility degree
\newcommandx{\coefficient}[3][1={\ray[s]}, 2=\ray, 3=\ray']{\alpha_{#2,#3}(#1)} % coefficient in linear dependence

@@

\title{Type-cones of $\b{g}$-vector fans}

@@

\begin{abstract}
We investigate the type-cone of the $\b{g}$-vector fans for different generalizations of the associahedron (hopefully generalized associahedra, gentle associahedra, graph associahedra, and maybe quotientopes and brick polytopes).
The objective is to determine which are the exchangeable pairs of objects that describe the type-cone.
When the type-cone happens to be simplicial, we derive simple descriptions of all polytopal realizations of the $\b{g}$-vector fan.
\end{abstract}

@@

\section{Polytopal realizations and type-cone of a simplicial fan}

@@

We denote by~$\R_{\ge0}\rays \eqdef \set{\sum_{\ray \in \rays} \lambda_{\ray} \, \ray}{\lambda_{\ray} \in \R_{\ge0}}$ the \defn{positive span} of a set~$\rays$ of vectors of~$\R^d$.
A \defn{polyhedral cone} is a subset of~$\R^d$ defined equivalently as the positive span of finitely many vectors or as the intersection of finitely many closed linear halfspaces.
The \defn{faces} of a cone~$C$ are the intersections of~$C$ with the supporting hyperplanes of~$C$.
The $1$-dimensional (resp.~codimension~$1$) faces of~$C$ are called~\defn{rays} (resp.~\defn{facets}) of~$C$.
A cone is \defn{simplicial} if it is generated by a set of linearly independent vectors.

@@

\subsection{Type-cone}

@@

\begin{proposition}
\label{prop:characterizationPolytopalFan}
Let~$\Fan$ be an essential complete simplicial fan in~$\R^n$. Then the following are equivalent for any height vector~$h \in \R^N$:
\begin{enumerate}
\item The fan~$\Fan$ is the normal fan of the polytope~$P_\b{h} \eqdef \set{\b{x} \in \R^n}{\b{G}\b{x} \le \b{h}}$.
\item For any two adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$ with~$\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$,
\[
\alpha \, h_{\ray} + \alpha' \, h_{\ray'} + \sum_{\ray[s] \in \rays \cap \rays'} \beta_{\ray[s]} \, h_{\ray[s]} > 0,
\]
where
\[
\alpha \, \ray + \alpha' \, \ray' + \sum_{\ray[s] \in \rays \cap \rays'} \beta_{\ray[s]} \, \ray[s] = 0
\]
is the unique (up to rescaling) linear dependence with~$\alpha, \alpha' > 0$ between the rays of~$\rays \cup \rays'$.
\end{enumerate}
\end{proposition}

@@

In this paper, we are interested in the set of all possible realizations of~$\Fan$ as the normal fan of a polytope~$P_\b{h}$. This was studied by P.~McMullen in~\cite{McMullen-typeCone} (see~\cite[Sect.~9.5]{DeLoeraRambauSantos} for a formulation in terms of chambers of triangulations of vector configurations).

\begin{definition}\label{def:typecone}
The \defn{type-cone} of~$\Fan$ is the cone~$\typeCone(\Fan)$ of all $\Fan$-admissible height vectors~$\b{h}$:
\begin{align*}
\typeCone(\Fan) & \eqdef \set{\b{h} \in \R^N}{\Fan \text{ is the normal fan of } P_\b{h}} \\
& = \Bigset{\b{h} \in \R^N}{\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} > 0 \; \begin{array}{l} \text{for any adjacent maximal} \\ \text{cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan$} \end{array}}.
\end{align*}
\end{definition}

Note that the type-cone is an open cone and contains a linearity subspace of dimension~$n$ (it is invariant by translation in~$\b{G} \R^n$). We could thus intersect~$\typeCone(\Fan)$ by the kernel of~$\b{G}$, or consider the projection~$\b{K}\typeCone(\Fan)$.

We denote by $\ctypeCone(\Fan)$ the closure of $\typeCone(\Fan)$. It is a closed polyhedral cone defined by the inequalities $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \geq 0$ for adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$.

\begin{remark}
 \label{rmk:non-simplicial}
Although we will only treat with simplicial fans, for completeness, note that \cref{prop:characterizationPolytopalFan} and \cref{def:typecone} can be easily adapted to non-simplicial fans. If~$\Fan$ is an arbitrary essential complete fan, it suffices to consider consider any simplicial refinement~$\Fan'$, and set some of the strict inequalities of the definition of $\typeCone(\Fan')$ to equality. Specifically, for any adjacent maximal cones~$\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ of~$\Fan'$ we impose
\[
 \sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} {\left\{\begin{array}{l} =\\ >\end{array}\right\}} 0
\]
with `$>$' when $\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ do not belong to the same maximal cone of $\Fan$; and with `$=$' if $\R_{\ge0}\rays$ and~$\R_{\ge0}\rays'$ belong to the same maximal cone of $\Fan$.
\end{remark}

\begin{definition}
An \defn{extremal adjacent pair} of~$\Fan$ is a pair of adjacent maximal cones~$\{\R_{\ge0}\rays, \R_{\ge0}\rays'\}$ of~$\Fan$ such that the corresponding inequality $\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \b{h}_{\ray[s]} \geq 0$ in the definition of the type-cone~$\ctypeCone(\Fan)$ actually defines a facet of~$\ctypeCone(\Fan)$.
\end{definition}
\arnau{I changed open to closed here}

In other words, extremal adjacent pairs define the extremal rays of the polar of the closed type-cone~$\ctypeCone(\Fan)$.
Understanding the extremal adjacent pairs of~$\Fan$ enables to describe its type-cone~$\typeCone(\Fan)$ and thus all its polytopal realizations.

\begin{remark}
\label{rem:dimTypeCone}
Since the type-cone is an $N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets.
We say that the type-cone is \defn{simplicial} when it has precisely $N-n$ facets.
\end{remark}

@@

\begin{definition}
\label{def:uerp}
We say that two exchangeable rays~$\ray, \ray'$ of~$\Fan$ admit a \defn{unique exchange relation} when the linear dependence
\[
\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \ray[s] = 0.
\]
does not depend on the pair~$\{\rays, \rays'\}$ of adjacent maximal cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, but only on the pair of rays~$\ray, \ray'$.
This implies in particular that the rays~$\ray[s]$ for which~$\coefficient[{\ray[s]}][\rays][\rays'] \ne 0$ belong to~$\rays \cup \rays'$ for any pair~$\{\rays, \rays'\}$ of adjacent cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$. These rays are thus called \defn{forced rays} for the exchangeable pair~$\{\ray, \ray'\}$.
\arnau{Remove definition of forced rays. Not used anywhere.}

We say that the fan~$\Fan$ has the \defn{unique exchange property} if any two exchangeable rays~$\ray, \ray'$ of~$\Fan$ admit a unique exchange relation.
\end{definition}

When~$\Fan$ has the unique exchange relation property, we change the notation~$\coefficient[{\ray[s]}][\rays][\rays']$ to~$\coefficient$ and we obtain that the type-cone of~$\Fan$ is expressed as
\[
\typeCone(\Fan) = \Bigset{\b{h} \in \R^N}{\sum_{\ray[s] \in \rays \cup \rays'} \coefficient \, \b{h}_{\ray[s]} > 0 \text{ for any exchangeable rays~$\ray$ and~$\ray'$ of~$\Fan$}}.
\]

\arnau{Do we have a notation for the set of all rays? I would change the sum over ${\ray[s] \in \rays \cup \rays'}$ to the whole ground set.}
\begin{definition}
In a fan~$\Fan$ with the unique exchange relation property, an \defn{extremal exchangeable pair} is a pair of exchangeable rays~$\{\ray,\ray'\}$ such that the corresponding inequality~${\sum_{\ray[s] \in \rays \cup \rays'} \coefficient \, \b{h}_{\ray[s]} \geq  0}$ defines a facet of the closed type-cone~$\ctypeCone(\Fan)$.
\end{definition}
\arnau{I changed open to closed here}

@@

In this section, we provide alternative polytopal realizations of the fan~$\Fan$.
We also discuss the behavior of these realizations in the situation when the type-cone~$\typeCone(\Fan)$ is simplicial.

@@

\begin{corollary}
\label{coro:simplicialTypeCone}
Assume that the type-cone~$\typeCone(\Fan)$ is simplicial and let~$\b{K}$ be the $(N-n) \times N$-matrix whose rows are the outer normal vectors of the facets of~$\typeCone(\Fan)$. Then the polytope
\[
R_\b{\ell} \eqdef \set{\b{z} \in \R^N}{K\b{z} = \b{\ell} \text{ and } \b{z} \ge 0}
\]
is a realization of the fan~$\Fan$ for any positive vector~$\b{\ell} \in \R_{>0}^{N-n}$.
Moreover, the polytopes~$R_\b{\ell}$ for~$\b{\ell} \in \R_{>0}^{N-n}$ describe all polytopal realizations of~$\Fan$.
\end{corollary}

\begin{proof}
Let~$\b{\ell} \in \R_{>0}^{N-n}$.
Since~$\b{K}$ has full rank there exists~$\b{h} \in \R^N$ such that~$\b{K}\b{h} = \b{\ell}$.
Since~$\b{K}\b{h} \ge 0$ and the rows of~$\b{K}$ are precisely all outer normal vectors of the facets of the type-cone~$\typeCone(\Fan)$, we obtain that~$\b{h}$ belongs to~$\typeCone(\Fan)$.
Since $R_\b{\ell} = Q_\b{h} \sim P_\b{h}$ by \cref{prop:alternativePolytopalRealization}, we conclude that~$R_\b{\ell}$ is a polytopal realization of~$\Fan$.
Since~$\typeCone(\Fan)$ is simplicial, we have~$\b{K}\typeCone(\Fan) = \R_{>0}^{N-n}$, so that we obtain all polytopal realizations of~$\Fan$ this way.
\end{proof}

@@

\subsection{Faces of the type-cone and Minkowski sums}
Recall that the \defn{Minkowski sum} of two polytopes $P$ and $Q$ is the polytope $P+Q=\set{p+q}{p\in P\text{ and } q\in Q}$.

@@

We say that~$P$ is a \defn{Minkowski summand} of~$R$ if there is a polytope~$Q$ such that $R=P+Q$, and a \defn{weak Minkowski summand} if there is a $\lambda\geq 0$ and a polytope~$Q$ such that $\lambda R=P+Q$. 
\cref{lem:MinkowskiSum} ensures that convex combinations in the type-cone correspond to Minkowski combinations of polytopes. Actually, the set of weak Minkowski summands of a polytope $P$ with normal fan~$\Fan$ is isomorphic to the closed type-cone~$\ctypeCone(\Fan)$ modulo linearity (the cone of weak Minkowski summands is studied by Meyer in~\cite{Meyer1974}, to see that it is equivalent to the type-cone and other formulations, see for example the appendix of~\cite{PostnikovReinerWilliams}).

This provides natural Minkowski summands for all polytopal realizations of~$\Fan$: the rays of the type-cone. These correspond to indecomposable polytopes~(cf.~\cite{Meyer1974} or \cite{McMullen-typeCone}). A polytope $P$ in $\R^n$ is 
  called \defn{indecomposable} if all its weak Minkowski summands are of the form $\lambda P+t$ for some $\lambda\geq 0$ and $t\in\R^n$.

\begin{corollary}
\arnau{See \cite{Meyer1974} and \cite{McMullen-typeCone}}
Any polytope in~$\typeCone(\Fan)$ is the Minkowski sum of at most~$N-n$ indecomposable polytopes corresponding to the rays of~$\b{K}\typeCone(\Fan)$.
\end{corollary}

If $P=Q+R$, then we say that $R$ is the \defn{Minkowski difference} of $P$ and $Q$, which we denote by $R=P-Q$. We will only consider the case where $Q$ is a summand of $P$.
There are two natural ways this construction generalizes to arbitrary pairs of polyhedra. On the one hand, we have $P-Q=\set{x\in\R^n}{x+Q\subseteq P}$. 
Notice that $P_\b{h}-P_{\b{h}'}=P_{\b{h} - \b{h'}}$ when $P_{\b{h}'}$ is a Minkowski summand of $P_\b{h}$. Considering arbitrary differences of support functions gives rise to  \defn{virtual polyhedra}, which is the Grothendieck group of the semigroup of polytopes with Minkowski sums~\cite{PukhlikovKhovanskii1992}.

\begin{corollary}
Let $\b{h}_1,\dots, \b{h}_{N-n}\in \ctypeCone(\Fan)$ form a basis of $\ker \b{G}$. Then every $P_\b{h}$ with $\b{h}\in \ctypeCone(\Fan)$ has a unique representation (up to translation) as a signed Minkowski sum of dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$.
\end{corollary}
\begin{proof}
 It suffices to express the projection of $\b{h}$ into $\ker\b{G}$ in terms of $\b{h}_1,\dots, \b{h}_{N-n}$, and to separate those terms with positive and negative coefficients to express Minkowski sums and differences.
\end{proof}

This is used in~\cite{ArdilaBenedettiDoker} to show that every generalized permutahedron can be written uniquelyas a signed Minkowski sum of simplices. 
\arnau{This has consequences in expressing volume and other valuations! I have to have a look at it.}
In the particular case when the type-cone is simplicial, then we can get rid of the sums.
\begin{corollary}
 If the type-cone~$\typeCone(\Fan)$ of $\Fan$ is simplicial, then the $N-n$ idecomposable polytopes $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$ arising from the rays of $\ctypeCone(\Fan)$
 verify that 
 \begin{enumerate}[(i)]
  \item  every $P_\b{h}$ with $\b{h}\in \typeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of positive dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$; and
 \item  every $P_\b{h}$ with $\b{h}\in \ctypeCone(\Fan)$ has a unique representation (up to translation) as a Minkowski sum of dilates of $P_{\b{h}_1},\dots, P_{\b{h}_{N-n}}$.
 \end{enumerate}

\end{corollary}
 Note that such a family of polytopes giving rise to unique positive representations only exists when the type-cone is simplicial.

\arnau{By \cite{McMullen-Valuations} valuations on the polytope $\alpha_1P_{\b{h}_1}+\cdots+\alpha_{N-n}P_{\b{h}_{N-n}}$ (such as volume) are a polynomial on $\alpha_1\dots\alpha_{N-n}$ with coefficients the mixed volumes. This also works when the $\alpha$'s are not necessarily positive \cite{ArdilaBenedettiDoker}. Does this help in any way?}

@@

In this section, we study the type-cones of complete simplicial fans arising as normal fans of three families of generalizations of the associahedron: the generalized associahedra of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI, FominZelevinsky-ClusterAlgebrasII, FominZelevinsky-ClusterAlgebrasIV, HohlwegLangeThomas, HohlwegPilaudStella}, the gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing}, and the graph associahedra~\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}. 
All these families contain the classical associahedra~$\Asso[n]$ constructed in~\cite{ShniderSternberg, Loday}.

@@

We first describe the associahedra of~\cite{ShniderSternberg, Loday} and their type-cones as they are the prototypes of our constructions.

@@

\subsubsection{Type-cones of associahedra}

From the linear dependencies of \cref{prop:exchangeablePairsAsso}, we obtain a redundant description of the type-cone of the fan~$\gvectorFan[n]$.

\begin{corollary}
\label{coro:typeConeAsso}
Let~$n \in \N$ and~$X(n) \eqdef \set{(a,b)}{0 \le a < b \le n+2}$. Then the type-cone of the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$ is given by
\[
\typeCone(\gvectorFan[n]) = \set{\b{h} \in \R^{X(n)}}{\begin{array}{l} \b{h}_{(0,n+2)} = 0, \qquad\text{and}\qquad \b{h}_{(a,a+1)} = 0 \text{ for all } 0 \le a \le n+1 \\ \b{h}_{(a,b)} + \b{h}_{(a',b')} > \b{h}_{(a,b')} + \b{h}_{(a',b)} \text{ for all } 0 \le a < a' < b < b' \le n+2 \end{array}}.
\]
\end{corollary}

We now describe the facets of this type-cone~$\typeCone(\gvectorFan[n])$.

@@

\begin{corollary}
\label{coro:simplicialTypeConeAsso}
The type-cone~$\typeCone(\gvectorFan[n])$ is simplicial.
\end{corollary}

@@

\begin{corollary}
\label{coro:simplicialTypeConeCA}
The type-cone~$\typeCone(\gvectorFan[n])$ is simplicial.
\end{corollary}
